Optimizing Abstract$^{\text 2}$ Machines

### 2012-11-11 paper/paper.tex
Comment out some old numbers.

Wide Store: cpu time: 551571 real time: 571319 gc time: 4003

@@

Lazy:
   cpu time: 32481 real time: 32881 gc time: 547

@@

Compile:
   cpu time: 255397 real time: 261532 gc time: 2947

\noindent
Compile + Lazy:
   cpu time: 31173 real time: 31642 gc time: 739

@@

Delta Store + Compile + Lazy:
   cpu time: 668 real time: 686 gc time: 41

>>>>

% Wide Store: cpu time: 551571 real time: 571319 gc time: 4003

@@

% Lazy:  cpu time: 32481 real time: 32881 gc time: 547

@@

% Compile: cpu time: 255397 real time: 261532 gc time: 2947

% \noindent
% Compile + Lazy: cpu time: 31173 real time: 31642 gc time: 739

@@

%% Delta Store + Compile + Lazy:
%%    cpu time: 668 real time: 686 gc time: 41
